RJObject Paper

### 2014-06-23 Documents/Paper/ms.tex
More bold

If $N' > N$, the extra parameters needed, $\{\xx_i\}_{i=N+1}^{N'}$,
are drawn from their prior conditional on the current value of the
hyperparameters, i.e. the interim prior $p(x | \hyperparams)$.

@@

Therefore, we allow an additional move that changes $\hyperparams$ to a new
value $\hyperparams'$, but rather than leaving the objects $\{\xx_i\}$ fixed, we
drag them so they represent the distribution $p(x | \hyperparams')$ rather than
$p(x|\hyperparams)$. We do this by making use of the transformation functions
$F(x; \hyperparams)$ and $G(x; \hyperparams)$ defined in Section~\ref{sec:proposal2}.

>>>>

If $N' > N$, the extra parameters needed, $\{\xx_i\}_{i=N+1}^{N'}$,
are drawn from their prior conditional on the current value of the
hyperparameters, i.e. the interim prior $p(\xx | \hyperparams)$.

@@

Therefore, we allow an additional move that changes $\hyperparams$ to a new
value $\hyperparams'$, but rather than leaving the objects $\{\xx_i\}$ fixed, we
drag them so they represent the distribution $p(\xx | \hyperparams')$ rather than
$p(\xx|\hyperparams)$. We do this by making use of the transformation functions
$F(x; \hyperparams)$ and $G(x; \hyperparams)$ defined in Section~\ref{sec:proposal2}.
